Efficient and Effective Metric Space Indexing for Complete Record Linkage

### 2017-11-20 paper.tex
Update on Overleaf.

\smallskip
\textbf{Traditional  blocking:}
In the traditional blocking technique records are blocked using hand selected keys as described in \cite{Chr12b}. The keys are chosen with the intention of giving the best possible results for the dataset. Multiple blocking keys are commonly used to address the problem of missing and erroneous values preventing matches from being found.

@@

\begin{table}[t]
\caption{Characteristics of data sets used in the experiments.}
 \label{table-datasets}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{cccc}
  \hline\noalign{\smallskip}
  Data set~ & ~Number of~ & ~Number of true~ & Attributes used \\
  name(s)  & records  & matching pairs & for traditional blocking \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA  & 1,295 & 17,184 & Title, authors, venue, year ? \\
  NCVR  & ~224,073 / 224,061~ & ~148,036~ & ? \\
  Isle of Skye & 32,567 & 2,900 & ? \\
  Kilmarnock  & 70852 & 8,300 & ? \\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}

>>>>

\smallskip
\textbf{Traditional  blocking:}
In the traditional blocking technique records are blocked using hand selected keys as described in \cite{Chr12b}. The keys are chosen with the intention of giving the best possible results for the dataset. Multiple blocking keys are commonly used to address the problem of missing and erroneous values preventing matches from being found. Often the choice of blocking keys requires intimate knowledge of the domain and of the records being linked.
fucky fuck fuck.

@@

\begin{table}[t]
\caption{Characteristics of data sets used in the experiments.}
 \label{table-datasets}
  \centering
  \begin{scriptsize}
  %\addtolength{\tabcolsep}{-0.5pt}
  \begin{tabular}{cccc}
  \hline\noalign{\smallskip}
  Data set~ & ~Number of~ & ~Number of true~ & Attributes used \\
  name(s)  & records  & matching pairs & for traditional blocking \\
  \noalign{\smallskip} \hline \noalign{\smallskip}
  CORA  & 1,295 & 17,184 & many-many & publication-publication\\
  NCVR  & ~448,134~ & ~148,036~ & 1:1  & voter-voter\\
  Isle of Skye & 32,567 & 2,900 & 1:1 * b\\
  Kilmarnock  & 70,852 & 8,300 & 1:1\\
  \noalign{\smallskip} \hline
  \end{tabular}
  \end{scriptsize}
\end{table}
